### 2020-04-14 dataclean.tex
readded sections with modified pdfs

To get some intuition for the GPU lifetimes on Titan, we give two views of
a hundred GPUs (Figure~\ref{fig:gpuview}) and a hundred locations
(Figure~\ref{fig:locview}). The GPU view is ``by serial number'' that
shows when each GPU was installed and removed at various locations as
well as its DBE and OTB events. The second view by location, shows
when different GPUs were installed and removed at a location, and
their OTB and DBE events.
\begin{figure}[ht]
  \includegraphics[width=6in]{figs/sample_sn.pdf}
  \caption{GPU serial number view of life and failures. Legend: black
    dots are installs, black lines are lifetimes at installed
    location, blue squares are OTB events, red triangles are DBE
    events, and black ] are ``last seen'' events.}
  \label{fig:gpuview}
\end{figure}
\begin{figure}[ht]
  \includegraphics[width=6in]{figs/sample_loc.pdf}
  \caption{GPU location view of life and failures.  Legend: black
    dots are installs, black lines are lifetimes at installed
    location, blue squares are OTB events, red triangles are DBE
    events, and black ] are ``last seen'' events.}
  \label{fig:locview}
\end{figure}
The serial number view clearly shows the two batches and the more
frequent OTB and DBE events in the old batch. It is also clear from
this view that most new GPUs stay at the initial install location
whereas the old GPUs were occasionally reinstalled at new locations.
The location view shows that each location was operational almost all
the time with small gaps when GPUs were changed out.

>>>>

To get some intuition for the GPU lifetimes on Titan, we give two views of
a hundred GPUs (Figure~\ref{fig:gpuview}) and a hundred locations
(Figure~\ref{fig:locview}). The GPU view is ``by serial number'' that
shows when each GPU was installed and removed at various locations as
well as its DBE and OTB events. The second view by location, shows
when different GPUs were installed and removed at a location, and
their OTB and DBE events.
\begin{figure*}[tb]
  \includegraphics[width=6.5in]{figs/sample_sn.pdf}
  \caption{GPU serial number view of life and failures. Legend: black
    dots are installs, black lines are lifetimes at installed
    location, blue squares are OTB events, red triangles are DBE
    events, and black ] are ``last seen'' events.}
  \label{fig:gpuview}
\end{figure*}
\begin{figure*}[tb]
  \includegraphics[width=6.5in]{figs/sample_loc.pdf}
  \caption{GPU location view of life and failures.  Legend: black
    dots are installs, black lines are lifetimes at installed
    location, blue squares are OTB events, red triangles are DBE
    events, and black ] are ``last seen'' events.}
  \label{fig:locview}
\end{figure*}
The serial number view clearly shows the two batches and the more
frequent OTB and DBE events in the old batch. It is also clear from
this view that most new GPUs stay at the initial install location
whereas the old GPUs were occasionally reinstalled at new locations.
The location view shows that each location was operational almost all
the time with small gaps when GPUs were changed out.
